
```{r by job specialisation}
  # top broad job specialisations
(broadjobspec_count <- count_freq(logistics_stack, target_cols = vars(broad_job_spec), totaln = nrow(logistics_jobs)))

(top10_broadjobspecs_plt <- hbar(broadjobspec_count %>% top_n(10), xvar = reorder(broad_job_spec, n), yvar = pct, xlab = "Top broad job specialisations", ylab = "Percentage share (%)", hjust_threshold = 0.4))

svpng(fname = "top10_broadjobspecs.png", plt = top10_broadjobspecs_plt, h = 5, w = 7)

  # top 10 job specialisations
(jobspec_count <- count_freq(logistics_stack, target_cols = vars(job_specialisation), totaln = nrow(logistics_jobs)))

(top10_jobspecs_plt <- hbar(jobspec_count %>% top_n(10), xvar = reorder(job_specialisation, n), yvar = pct, xlab = "Top job specialisations", ylab = "Percentage share (%)", hjust_threshold = 0.2))

svpng(fname = "top10_jobspecs.png", plt = top10_jobspecs_plt, h = 5, w = 7)

  # top 3 for job specialisations for major broad_job_spec
top3_jobsspecs <- count_freq(logistics_stack %>% filter(broad_job_spec %in% broadjobspec_count$broad_job_spec[broadjobspec_count$pct >= 0.04]), target_cols = vars(broad_job_spec, job_specialisation), group_vars = vars(broad_job_spec)) %>%
  mutate(grp_n = sum(n),
         broad_job_spec = paste0(broad_job_spec, " (n=", grp_n, ")")) %>% 
  slice_max(order_by = n, n = 3) %>% 
  ungroup() %>% 
  mutate(order = max(row_number()) - row_number())

(top3_jobsspecs_plt <- top3_jobsspecs %>% 
  ggplot(aes(x = order, y = pct, fill = broad_job_spec)) +
  geom_col() +
  facet_wrap(facets = vars(reorder(broad_job_spec, - n)), scales = "free_y", nrow = 2) +
  geom_text(aes(label = sprintf("%.1f", pct * 100), 
                hjust = ifelse(pct >= 0.5, 1, 0))) +
  coord_flip() +
  labs(x = "Job specialisation", y = "Percentage share (%)") +
  scale_y_continuous(labels = function(x) round(x * 100, 0)) +
  scale_x_continuous(breaks = top3_jobsspecs$order, labels = str_wrap(top3_jobsspecs$job_specialisation, width = 15)) +
  theme(legend.position = "none"))

svpng(fname = "top3_jobspecs_bybroadjobspecs.png", plt = top3_jobsspecs_plt, h = 5, w = 9)

# (jobspecs_cbplt <- (top10_broadjobspecs_plt | top3_jobsspecs_plt) +
#   plot_layout(widths = c(1, 3)) +
#   plot_annotation(tag_levels = 'A'))
# 
# svpng(fname = "top_jobspecs_cbplt.png", plt = jobspecs_cbplt, w = 12, h = 6)
```

```{r high-value jobs - by min qualification}
# Most jobs are at degree and diploma levels
(min_qualif_count <- count_freq(logistics_jobs %>% filter(min_qualification != "Not Specified"), target_cols = vars(min_qualification)))
# count_freq(logistics_jobs, target_cols = vars(min_qualification))

(min_qualif_plt <- hbar(df = min_qualif_count, xvar = reorder(min_qualification, n), yvar = pct, xlab = "Min. qualification", ylab = "Percentage share (%)", hjust_threshold = .3))

svpng(fname = "min_qualification.png", plt = min_qualif_plt, w = 6, h = 5)

# Only 12% of the entry-level jobs are for the Bachelor's holder, which means these graduates may face underemployment since their jobs don't need such level of education.
  # exclude 1239 rows where position_level == "Not Specified" since the corresponding min_qualification are all "Not Specified" too
(pos_minqualif_count <- count_freq(logistics_jobs %>% filter(position_level != "Not Specified"), target_cols = vars(position_level, min_qualification), group_vars = vars(position_level)))

(pos_minqualif_plt <- stacked_hbar(df = pos_minqualif_count, xvar = fct_rev(position_level), yvar = pct, fillvar = min_qualification, xlab = "Position level", ylab = "Percentage share (%)", fill_lab = "Min. qualification"))

svpng(fname = "pos_minqualif.png", plt = pos_minqualif_plt, w = 6, h = 6)

# On the other hand, if Diploma or Bachelor's graduates wants to work in jobs with equivalent levels, they need at least 1-2-year experiences 
(minqualif_pos_count <- count_freq(logistics_jobs %>% filter(position_level != "Not Specified"), target_cols = vars(min_qualification, position_level), group_vars = vars(min_qualification)))

(minqualif_pos_plt <- stacked_hbar(df = minqualif_pos_count, xvar = fct_rev(min_qualification), yvar = pct, fillvar = position_level, xlab = "Min. qualification", ylab = "Percentage share (%)", fill_lab = "Position level", ncol = 2))

svpng(fname = "minqualif_pos.png", plt = minqualif_pos_plt, w = 6, h = 6)
```

```{r broad_job_spec and min qualification}
# to see the high-value jobs in each broad_job_spec
(top10_broadjobspecs <- (broadjobspec_count %>% top_n(10))$broad_job_spec)

(qualif_bybjobspec_count <- count_freq(logistics_stack %>% filter(min_qualification != "Not Specified"), target_cols = vars(broad_job_spec, min_qualification), group_vars = vars(broad_job_spec)))

qualif_bybjobspec_count$broad_job_spec <- factor(qualif_bybjobspec_count$broad_job_spec, levels = levels(reorder(broadjobspec_count$broad_job_spec, broadjobspec_count$n)))

(qualif_bybjobspec_plt <- qualif_bybjobspec_count %>% filter(!is.na(broad_job_spec)) %>% 
  ggplot(aes(x = broad_job_spec, y = pct, fill = fct_rev(min_qualification))) +
  geom_col() +
  geom_text(aes(label = ifelse(pct <=0.1, "", sprintf("%.1f", pct * 100))), position =  position_stack(vjust = 0.5)) +
  coord_flip() +
  scale_y_continuous(labels = function(x) round(x * 100, 0)) +
  scale_fill_brewer(palette = "Greens") +
  labs(x = "Broad job specialisation", y = "Percentage share (%)", fill = "Min. qualification") +
    theme(legend.position = "bottom",
          legend.text = element_text(size = 8)) +
    guides(fill = guide_legend(title.position = "top",
                               ncol = 2)))

svpng(fname = "qualif_bybroadjobspec.png", plt = qualif_bybjobspec_plt, w = 6, h = 6)

  # by job specialisation and broad min. qualification
(broadqualif_bybroadjobspec_count <- count_freq(logistics_stack %>% filter(min_qualification != "Not Specified" & broad_job_spec %in% top10_broadjobspecs), target_cols = vars(broad_job_spec, min_qualification_broad), group_vars = vars(broad_job_spec)))

broadqualif_bybroadjobspec_count$broad_job_spec <- factor(broadqualif_bybroadjobspec_count$broad_job_spec, levels = top10_broadjobspecs)

(broadqualif_bybroadjobspec_plt <- stacked_hbar(df = broadqualif_bybroadjobspec_count, xvar = fct_rev(broad_job_spec), yvar = pct, fillvar = min_qualification_broad, xlab = "Top broad job specialisations", ylab = "Percentage share (%)", fill_lab = "Min. qualification category", ncol = 3))

svpng(fname = "broadqualif_bybroadjobspec.png", plt = broadqualif_bybroadjobspec_plt, w = 6, h = 6)
```

```{r top 10 job specialisations and min qualification}
# to see the high-value jobs in each broad_job_spec

(top10_jobspecs <- (jobspec_count %>% top_n(10))$job_specialisation)

(qualif_byjobspec_count <- count_freq(logistics_stack %>% filter(min_qualification != "Not Specified" & job_specialisation %in% top10_jobspecs), target_cols = vars(job_specialisation, min_qualification), group_vars = vars(job_specialisation)))

qualif_byjobspec_count$job_specialisation <- factor(qualif_byjobspec_count$job_specialisation, levels = levels(reorder(jobspec_count$job_specialisation[jobspec_count$job_specialisation %in% top10_jobspecs], jobspec_count$n[jobspec_count$job_specialisation %in% top10_jobspecs])))

(qualif_byjobspec_plt <- qualif_byjobspec_count %>% 
  ggplot(aes(x = job_specialisation, y = pct, fill = fct_rev(min_qualification))) +
  geom_col() +
  geom_text(aes(label = ifelse(pct <=0.1, "", sprintf("%.1f", pct * 100))), position =  position_stack(vjust = 0.5)) +
  coord_flip() +
  scale_y_continuous(labels = function(x) round(x * 100, 0)) +
  scale_fill_brewer(palette = "Greens") +
  labs(x = "Top 10 job specialisations", y = "Percentage share (%)", fill = "Min. qualification") +
    theme(legend.position = "bottom",
          legend.text = element_text(size = 8)) +
    guides(fill = guide_legend(title.position = "top",
                               ncol = 2)))

svpng(fname = "qualif_byjobspec.png", plt = qualif_byjobspec_plt, w = 6, h = 6)

  # by job specialisation and broad min. qualification
(broadqualif_byjobspec_count <- count_freq(logistics_stack %>% filter(min_qualification != "Not Specified" & job_specialisation %in% top10_jobspecs), target_cols = vars(job_specialisation, min_qualification_broad), group_vars = vars(job_specialisation)))

broadqualif_byjobspec_count$job_specialisation <- factor(broadqualif_byjobspec_count$job_specialisation, levels = top10_jobspecs)

(broadqualif_byjobspec_plt <- stacked_hbar(df = broadqualif_byjobspec_count, xvar = fct_rev(job_specialisation), yvar = pct, fillvar = min_qualification_broad, xlab = "Top 10 job specialisations", ylab = "Percentage share (%)", fill_lab = "Min. qualification category", ncol = 3))

svpng(fname = "broadqualif_byjobspec.png", plt = broadqualif_byjobspec_plt, w = 6, h = 6)
```

We also analyse jobs that didn't specify the educational qualifications.
```{r min qualification NA - by position level}
bypos_ttl <- count_freq(logistics_jobs, target_cols = vars(position_level)) %>% rename(ttl_n = n)

(bypos_minqualifNA <- count_freq(logistics_jobs %>% filter(min_qualification == "Not Specified"), target_cols = vars(position_level)) %>% 
    # combine with min_qualifNA to see which pos level has the highest share of non-specified qualif
    left_join(bypos_ttl %>% select(-pct), by = "position_level") %>% mutate(NApct = n/ttl_n))
    
```

```{r min qualification NA - by job specialisation}
byjobspecs_ttl <- logistics_stack %>% count_freq(target_cols = vars(job_specialisation)) %>% rename(ttl_n = n)

logistics_stack %>% filter(min_qualification == "Not Specified") %>% count_freq(target_cols = vars(job_specialisation)) %>% 
  left_join(byjobspecs_ttl %>% select(-pct), by = "job_specialisation") %>% 
  mutate(NApct = n/ttl_n) #%>% arrange(-NApct)
```

```{r min qualification NA - by industry}
byind_ttl <- logistics_jobs %>% count_freq(target_cols = vars(industry)) %>% rename(ttl_n = n)

logistics_jobs %>% filter(min_qualification == "Not Specified") %>% 
  count_freq(target_cols = vars(industry)) %>% 
  left_join(byind_ttl %>% select(-pct), by = "industry") %>% 
  mutate(NApct = n/ttl_n)
```

```{r min qualification NA - types of job}
popular_jobs_byjobspec(dframe = logistics_jobs, is_filter = T, num_token = 2, js_var = min_qualification, js_selected = "Not Specified", topn = 10)
```


```{r by position level}
# Most jobs are at least Junior position which requires 1-2 years of experience, entry-level jobs only accounted for 11%.
count_freq(logistics_jobs, target_cols = vars(position_level))
count_freq(logistics_jobs %>% filter(position_level != "Not Specified"), target_cols = vars(position_level))

```

```{r % of position level by job specialisation}
(pos_byjobspec_count <- count_freq(logistics_stack %>% filter(position_level != "Not Specified"), target_cols = vars(broad_job_spec, position_level), group_vars = vars(broad_job_spec)))

pos_byjobspec_count$broad_job_spec <- factor(pos_byjobspec_count$broad_job_spec, levels = levels(reorder(broadjobspec_count$broad_job_spec, broadjobspec_count$n)))

(pos_byjobspec_plt <- pos_byjobspec_count %>% filter(!is.na(broad_job_spec)) %>% 
  ggplot(aes(x = broad_job_spec, y = pct, fill = fct_rev(position_level))) +
  geom_col() +
  geom_text(aes(label = ifelse(pct <=0.1, "", sprintf("%.1f", pct * 100))), position =  position_stack(vjust = 0.5)) +
  coord_flip() +
  scale_y_continuous(labels = function(x) round(x * 100, 0)) +
  scale_fill_brewer(palette = "Greens") +
  labs(x = "Broad job specialisation", y = "Percentage share (%)", fill = "Position level") +
    theme(legend.position = "bottom") +
    guides(fill = guide_legend(title.position = "top")))

svpng(fname = "pos_byjobspec.png", plt = pos_byjobspec_plt, h = 6, w = 6)
```

```{r by years of experience}
# Most jobs require 1-2 years (corresponding to Junior Exe.), and 3 and 5 years (Senior Exe.) 
count_freq(logistics_jobs, target_cols = vars(years_of_experience))

# Most Junior Executive jobs require 1-2 years of experience
count_freq(logistics_jobs %>% filter(position_level == "Junior Executive"), target_cols = vars(years_of_experience))

# Senior Executive jobs require 3-5 years of experience 
count_freq(logistics_jobs %>% filter(position_level == "Senior Executive"), target_cols = vars(years_of_experience))

# Entry level
# Senior Executive jobs require 3-5 years of experience 
count_freq(logistics_jobs %>% filter(position_level == "Entry Level"), target_cols = vars(years_of_experience))

# Most jobs not specifying years of experience are from the Entry Level and Non-Executive levels
count_freq(logistics_jobs %>% filter(years_of_experience == ""), target_cols = vars(position_level))
```

```{r by industry}
# which industries have the most logistics jobs?
count_freq(logistics_jobs, target_cols = vars(industry))

# which industries have the most high-value jobs?
count_freq(logistics_jobs %>% filter(min_qualification %in% c("Diploma", "Bachelor's Degree", "Master's Degree")), target_cols = vars(industry))
```

```{r popular jobtitles function}
test_fn <- function(dframe, is_filter = F, js_var = NULL){
  
}

popular_jobs_byjobspec <- function(dframe = logistics_stack, is_filter = F, num_token = 2, js_var = NULL, js_selected = NULL, topn = 5, plt_title = "", label_threshold = 50){
  ## this function counts top n job titles in certain (broad) job specs and plot
  
  # js_var: variable name (no quotation mark). It's either `broad_job_spec` or `job_specialisation`
  # js_selected: a vector in format of `c()`. Can be broad_job_spec (if is_broad == T), and job_specialisation otherwise. 
  # topn: integer, top n job titles for each broad_job_spec or job_specialisation
  
  js_var <- enquo(js_var)
  
  if (is_filter){
    dframe <- dframe %>% filter(!!js_var %in% js_selected)
  }
  
  # split job titles into bitokens for the specific (broad) job specialisations selected
  js_tokens <- tokenization(dframe, col = "job_title", num_tokens = num_token, lemma = F, custom_stopwords = c("career", "fair", "jobstreet", "11th", "march", "9", "bayan", "lepas", "techâ", "2022", "virtual", "fresh", "graduate"))[[2]]
  
  # filter rows which contain the top job titles
  popular_jobtitles <- dframe %>% 
    filter(grepl(paste(js_tokens[1:topn, ]$word, collapse = "|"), job_title, ignore.case = T))
  
  # count the frequencies for each job_title (containing the tokens)
  popular_jobtitles_js_count <- as_tibble(data.frame(matrix(nrow = topn, ncol = 2)))
  colnames(popular_jobtitles_js_count) <- c("job_title", "n")
  popular_jobtitles_js_count$job_title <- js_tokens[1:topn,]$word
  popular_jobtitles_js_count$n <- as.double(popular_jobtitles_js_count$n)
  for (i in 1:topn){
    count <- popular_jobtitles %>% filter(grepl(js_tokens[i,]$word, job_title, ignore.case = T)) %>% nrow()
    popular_jobtitles_js_count[i, ]$n <- count
  }
  
  # plot
  topn_jobtitles_js_plt <- hbar(df = popular_jobtitles_js_count, xvar = reorder(job_title, n), yvar = n, xlab = "Top job titles", ylab = "Count", is_pct = F, title = plt_title, hjust_threshold = label_threshold)
  
  return(list(js_tokens, popular_jobtitles_js_count, topn_jobtitles_js_plt))
}
```

```{r type of jobs - overall}
# what are the major logistics job titles? Use keywords
  # overall popular job titles
(top10_jobtitles_overall_plt <- popular_jobs_byjobspec(dframe = logistics_jobs, is_filter = F, topn = 10, plt_title = "", label_threshold = 40)[[3]])

svpng(fname = "top10_jobtitles_overall.png", plt = top10_jobtitles_overall_plt, h = 7, w = 7)
```

```{r type of jobs - high-skilled/tertiary qualification}
popular_jobs_byjobspec(dframe = logistics_jobs %>% filter(min_qualification_broad == "High-skilled"), is_filter = F, topn = 10, plt_title = "", label_threshold = 90)[[1]]

(top10_tertiaryjobtitles_overall_plt <- popular_jobs_byjobspec(dframe = logistics_jobs %>% filter(min_qualification_broad == "High-skilled"), is_filter = F, topn = 10, plt_title = "", label_threshold = 20)[[3]])

svpng(fname = "top10_tertiaryjobtitles_overall.png", plt = top10_tertiaryjobtitles_overall_plt, h = 7, w = 7)

logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("supply chain", job_title, ignore.case = T)) %>% view()

  # what are the position levels for "customer service" and "supply chain" jobs?
count_freq(data = logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("supply chain", job_title, ignore.case = T)), target_cols = vars(position_level))

count_freq(data = logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("production planner", job_title, ignore.case = T)), target_cols = vars(position_level))
```

```{r skills required by tertiary production planner jobs}
tokenization(data = logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("production planner", job_title, ignore.case = T) & !is.na(job_description)), col = "job_description", num_tokens = 1)[[2]]

tokenization(data = logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("production planner", job_title, ignore.case = T) & !is.na(job_description)), col = "job_description", num_tokens = 2)[[2]]

tokenization(data = logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("production planner", job_title, ignore.case = T) & !is.na(job_description)), col = "job_description", num_tokens = 3)[[2]]
```

```{r skills required by tertiary supply chain jobs}
tokenization(data = logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("supply chain", job_title, ignore.case = T) & !is.na(job_description)), col = "job_description", num_tokens = 1)[[2]]

tokenization(data = logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("supply chain", job_title, ignore.case = T) & !is.na(job_description)), col = "job_description", num_tokens = 2)[[2]] #%>% filter(grepl("skill", word))

tokenization(data = logistics_jobs %>% filter(min_qualification_broad == "High-skilled" & grepl("supply chain", job_title, ignore.case = T) & !is.na(job_description)), col = "job_description", num_tokens = 3)[[2]]
```

```{r type of jobs by industry}
count_freq(data = logistics_jobs, target_cols = vars(industry))

# logistics_inds <- c("Transportation / Logistics", "General & Wholesale Trading", "Retail / Merchandise")
count_freq(data = logistics_jobs %>% filter(industry %in% c("Transportation / Logistics")), target_cols = vars(industry, min_qualification), group_vars = vars(industry))

count_freq(data = logistics_jobs %>% filter(industry %in% c("Transportation / Logistics")), target_cols = vars(industry, position_level), group_vars = vars(industry))
```

```{r type of jobs by broad job specialisation}
  # broad_job_spec == "Manufacturing"
(top5_jobtitles_manuf_plt <- popular_jobs_byjobspec(js_var = broad_job_spec, js_selected = c("Manufacturing"), topn = 5, plt_title = "(a) Manufacturing", label_threshold = 90)[[3]])

  # broad_job_spec == "Services"
(top5_jobtitles_serv_plt <- popular_jobs_byjobspec(js_var = broad_job_spec, js_selected = c("Services"), topn = 5, plt_title = "(b) Services", label_threshold = 90)[[3]])

  # broad_job_spec == "Sales/Marketing"
(top5_jobtitles_sales_plt <- popular_jobs_byjobspec(js_var = broad_job_spec, js_selected = c("Sales/Marketing"), topn = 5, plt_title = "(c) Sales/Marketing", label_threshold = 30)[[3]])

(top5_jobtitle_cbplt <- (top5_jobtitles_manuf_plt | top5_jobtitles_serv_plt) / (top5_jobtitles_sales_plt | plot_spacer())) +
  plot_layout(widths = c(1, 1))

svpng(fname = "top5_jobtitles_bybroadjobspec_cbplt.png", plt = top5_jobtitle_cbplt, h = 7, w = 7)

  # check what's associated with "supply chain"
logistics_jobs %>% filter(grepl("supply chain", job_title, ignore.case = T)) %>% view()
logistics_jobs %>% filter(grepl("customer service", job_title, ignore.case = T)) %>% view()
```


```{r type of high-value jobs by broad job specs}
(top5_jobtitles_computer_plt <- popular_jobs_byjobspec(num_token = 1, js_var = broad_job_spec, js_selected = c("Computer/Information Technology"), topn = 5, plt_title = "Computer/Information Technology", label_threshold = 90)[[3]])

(top5_jobtitles_accfin_plt <- popular_jobs_byjobspec(num_token = 1, js_var = broad_job_spec, js_selected = c("Accounting/Finance"), topn = 5, plt_title = "Accounting/Finance", label_threshold = 90)[[3]])

(top5_jobtitles_engineering_plt <- popular_jobs_byjobspec(num_token = 1, js_var = broad_job_spec, js_selected = c("Engineering"), topn = 5, plt_title = "Engineering", label_threshold = 90)[[3]])

(top5_jobtitles_building_plt <- popular_jobs_byjobspec(num_token = 1, js_var = broad_job_spec, js_selected = c("Building/Construction"), topn = 5, plt_title = "Building/Construction", label_threshold = 90)[[3]])
```

```{r type of jobs by top job specialisations}
  # broad_job_spec == "Manufacturing"
(top5_jobtitles_manuf_plt2 <- popular_jobs_byjobspec(js_var = job_specialisation, js_selected = c("Manufacturing"), topn = 5, plt_title = "(a) Manufacturing", label_threshold = 90)[[3]])

  # broad_job_spec == "Purchasing/Material Mgmt"
(top5_jobtitles_purchasing_plt <- popular_jobs_byjobspec(js_var = job_specialisation, js_selected = c("Purchasing/Material Mgmt"), topn = 5, plt_title = str_wrap("(b) Purchasing/Material Mgmt", width = 20), label_threshold = 18)[[3]])

  # broad_job_spec == "Logistics/Supply Chain"
(top5_jobtitles_logistics_plt <- popular_jobs_byjobspec(js_var = job_specialisation, js_selected = c("Logistics/Supply Chain"), topn = 5, plt_title = "(c) Logistics/Supply Chain", label_threshold = 30)[[3]])

(top5_jobtitle_cbplt2 <- (top5_jobtitles_manuf_plt2 | top5_jobtitles_purchasing_plt) / (top5_jobtitles_logistics_plt | plot_spacer())) +
  plot_layout(widths = c(1, 1))

svpng(fname = "top5_jobtitles_byjobspec_cbplt.png", plt = top5_jobtitle_cbplt2, h = 7, w = 7)

  # check what's associated with "supply chain"
logistics_jobs %>% filter(grepl("supply chain", job_title, ignore.case = T)) %>% view()
logistics_jobs %>% filter(grepl("customer service", job_title, ignore.case = T)) %>% view()
```

```{r type of jobs by top job specialisations and min_qualification_broad}
  
skills_levels <- c("Low-skilled", "Mid-skilled", "High-skilled")
main_jobspecs <- (jobspec_count %>% top_n(3))$job_specialisation
# [1] "Purchasing/Material Mgmt" "Logistics/Supply Chain"   "Manufacturing"

top_jobtitles_jsqualif <- as_tibble_row(list(job_title = NA, n = NA, job_specialisation = NA, min_qualification_broad = NA))
for (s in skills_levels){
  for (js in main_jobspecs) {
    top_jobtitles_jsqualif <- top_jobtitles_jsqualif %>% 
      bind_rows(
        popular_jobs_byjobspec(dframe = logistics_stack %>% filter(min_qualification_broad == s), is_filter = T, js_var = job_specialisation, js_selected = js, topn = 5)[[2]] %>% 
          mutate(job_specialisation = js, min_qualification_broad = s)
        )
  }
}
top_jobtitles_jsqualif <- top_jobtitles_jsqualif %>% filter(!is.na(job_title)) %>% filter(n != 0) %>% 
  arrange(job_specialisation, min_qualification_broad, -n) %>% 
  mutate(order = max(row_number()) - row_number())

top_jobtitles_jsqualif$job_specialisation <- factor(top_jobtitles_jsqualif$job_specialisation, levels = main_jobspecs)
top_jobtitles_jsqualif$min_qualification_broad <- factor(top_jobtitles_jsqualif$min_qualification_broad, levels = skills_levels)

(top_jobtitles_jsqualif_plt <- top_jobtitles_jsqualif %>% 
  ggplot(aes(x = order, y = n, fill = job_specialisation)) +
  geom_col() +
  coord_flip() +
  facet_wrap(facets = vars(job_specialisation, min_qualification_broad), scales = "free_y", labeller = labeller(job_specialisation =  label_wrap_gen(width = 15, multi_line = F))) +
  scale_x_continuous(breaks = top_jobtitles_jsqualif$order, labels = str_wrap(top_jobtitles_jsqualif$job_title, width = 20)) +
  labs(x = "Top job titles", y = "Count") +
  theme(legend.position = "none"))

svpng(fname = "top_jobtitles_jsqualif.png", plt = top_jobtitles_jsqualif_plt, h = 10, w = 10)
```

```{r type of jobs by top job specialisations and min_qualification_broad - detailed}
  # detailed look at differences among skill levels - Purchasing/Material Mgmt
# High-skilled have more managerial positions
logistics_stack %>% filter(job_specialisation == "Purchasing/Material Mgmt" & grepl(paste((top_jobtitles_jsqualif %>% filter(job_specialisation == "Purchasing/Material Mgmt" & min_qualification_broad == "Mid-skilled"))$job_title, collapse = "|"), job_title, ignore.case = T)) %>% count(position_level) %>% ungroup() %>% mutate(pct = n/sum(n))

logistics_stack %>% filter(job_specialisation == "Purchasing/Material Mgmt" & grepl(paste((top_jobtitles_jsqualif %>% filter(job_specialisation == "Purchasing/Material Mgmt" & min_qualification_broad == "High-skilled"))$job_title, collapse = "|"), job_title, ignore.case = T)) %>% count(position_level) %>% ungroup() %>% mutate(pct = n/sum(n))

  # Logistics/Supply Chain
logistics_stack %>% filter(job_specialisation == "Logistics/Supply Chain" & min_qualification_broad == "Low-skilled" & grepl(paste((top_jobtitles_jsqualif %>% filter(job_specialisation == "Logistics/Supply Chain" & min_qualification_broad == "Low-skilled"))$job_title, collapse = "|"), job_title, ignore.case = T)) %>% view()

logistics_stack %>% filter(job_specialisation == "Logistics/Supply Chain" & min_qualification_broad == "Mid-skilled" & grepl(paste((top_jobtitles_jsqualif %>% filter(job_specialisation == "Logistics/Supply Chain" & min_qualification_broad == "Mid-skilled"))$job_title, collapse = "|"), job_title, ignore.case = T)) %>% view()

logistics_stack %>% filter(job_specialisation == "Logistics/Supply Chain" & min_qualification_broad == "High-skilled" & grepl(paste((top_jobtitles_jsqualif %>% filter(job_specialisation == "Logistics/Supply Chain" & min_qualification_broad == "High-skilled"))$job_title, collapse = "|"), job_title, ignore.case = T)) %>% view()
```

```{r}
logistics_stack %>% filter(grepl("engineer", job_title, ignore.case = T) & broad_job_spec == "Engineering") %>% view()

logistics_stack %>% filter(grepl("analyst | business | consultant", job_title, ignore.case = T) & broad_job_spec == "Computer/Information Technology") %>% view()

logistics_stack %>% filter(grepl("manager | assistant | account", job_title, ignore.case = T) & broad_job_spec == "Accounting/Finance") %>% view()
```

```{r highly growth job specialisations}
(uniq_companies_bysizejs_count <- logistics_stack %>% filter(!is.na(company_size)) %>% distinct_at(c("company_name", "job_specialisation"), .keep_all = T) %>% 
  count(company_size, job_specialisation, sort = T) %>% 
  rename(num_uniq_companies = n))

topn_jobspecs <- (jobspec_count %>% top_n(5))$job_specialisation

(av_postings_bysizejs <- logistics_stack %>% 
    filter(!is.na(company_size)) %>% 
    group_by(company_size, job_specialisation) %>% 
    summarise(total_postings = n()) %>% 
    left_join(uniq_companies_bysizejs_count) %>% 
    mutate(av_postings = total_postings / num_uniq_companies)  %>% 
    filter(job_specialisation %in% topn_jobspecs) %>% 
    ungroup() %>% group_by(company_size) %>% 
    mutate(med_postings = median(av_postings)))

av_postings_bysizejs$job_specialisation <- factor(av_postings_bysizejs$job_specialisation, levels = topn_jobspecs)

  # the vertical line is the median for each group among the top 5 job specialisations
(size_bytop5_jobspec_plt <- hbar(df = av_postings_bysizejs, xvar = fct_rev(job_specialisation), yvar = av_postings, is_pct = F, hjust_threshold = 1.0) + 
           facet_wrap(facets = vars(company_size), scales = "free_x") +
           geom_hline(aes(yintercept = med_postings), linetype = "dotted", color = "gray30", size = 0.4))

svpng(fname = "size_bytop5_jobspec.png", plt = size_bytop5_jobspec_plt, h = 10, w = 7)
```


```{r job specialisation by min_qualification_broad}
(top3_jobsspecs_bybroadminqualif <- count_freq(logistics_stack, target_cols = vars(min_qualification_broad, job_specialisation), group_vars = vars(min_qualification_broad)) %>%
  mutate(grp_n = sum(n),
         min_qualification_broad = paste0(min_qualification_broad, " (n=", grp_n, ")")) %>% 
  slice_max(order_by = n, n = 3) %>% 
  ungroup() %>% 
  mutate(order = max(row_number()) - row_number()))

(top3_jobsspecs_bybroadminqualif_plt <- top3_jobsspecs_bybroadminqualif %>% 
  ggplot(aes(x = order, y = pct, fill = min_qualification_broad)) +
  geom_col() +
  facet_wrap(facets = vars(reorder(min_qualification_broad, - n)), scales = "free_y", nrow = 2) +
  geom_text(aes(label = sprintf("%.1f", pct * 100), 
                hjust = ifelse(pct >= 0.25, 1, 0))) +
  coord_flip() +
  labs(x = "Job specialisation", y = "Percentage share (%)") +
  scale_y_continuous(labels = function(x) round(x * 100, 0)) +
  scale_x_continuous(breaks = top3_jobsspecs_bybroadminqualif$order, labels = str_wrap(top3_jobsspecs_bybroadminqualif$job_specialisation, width = 15)) +
  theme(legend.position = "none"))

svpng(fname = "top3_jobspecs_bybroadminqualif.png", plt = top3_jobsspecs_bybroadminqualif_plt, h = 5, w = 9)
```


# salary
81% of the job postings didn't specify the salary.
```{r % salary NA}
sum(logistics_jobs$salary == "") / nrow(logistics_jobs)
```

Low-level positions are more likely to reveal salary. The salary analysed might be lower than the actual situation.
Therefore, it's better to use weighted average.
```{r salary NA - by position level}
# bypos_ttl <- count_freq(logistics_jobs, target_cols = vars(position_level)) %>% rename(ttl_n = n)

(bypos_salaryNA <- count_freq(logistics_jobs %>% filter(salary == ""), target_cols = vars(position_level)) %>% 
    # combine with bypos_ttl to see which pos level has the highest share of non-specified qualif
    left_join(bypos_ttl %>% select(-pct), by = "position_level") %>% mutate(NApct = n/ttl_n))
    
```

Again, jobs with higher % of high-skilled jobs have higher missing salaries (~80%). General and clerical work lower (~60%).
```{r salary NA - by job specialisation}
# byjobspecs_ttl <- logistics_stack %>% count_freq(target_cols = vars(job_specialisation)) %>% rename(ttl_n = n)

logistics_stack %>% filter(salary == "") %>% count_freq(target_cols = vars(job_specialisation)) %>% 
  left_join(byjobspecs_ttl %>% select(-pct), by = "job_specialisation") %>% 
  mutate(NApct = n/ttl_n) #%>% arrange(-NApct)
```

```{r salary NA - by industry}
# byind_ttl <- logistics_jobs %>% count_freq(target_cols = vars(industry)) %>% rename(ttl_n = n)

logistics_jobs %>% filter(salary == "") %>% 
  count_freq(target_cols = vars(industry)) %>% 
  left_join(byind_ttl %>% select(-pct), by = "industry") %>% 
  mutate(NApct = n/ttl_n)
```

```{r min qualification NA - types of job}
popular_jobs_byjobspec(dframe = logistics_jobs, is_filter = T, num_token = 2, js_var = min_qualification, js_selected = "Not Specified", topn = 10)
```

















